### 2014-11-12 tex/javalite.tex
updates to javalite and fixed missing paren in CL definition in surface syntax

\section{Javalite}
The algorithm for generalized symbolic execution with symbolic heaps
is presented using Javalite. Javalite is a syntactic machine defined
as rewrites on a string \cite{saints-MS}. The semantics are small-step
using a CESK model with a (C)ontrol string representing the expression
being evaluated, an (E)nvironment for local variables, a (S)tore for
the heap, and a (K)ontinuation for what is to be executed next. The
semantics of the original Javalite machine, and its machine syntax,
are changed to reflect generalized symbolic execution and then
generalized execution with symbolic heaps.

The surface syntax (input) for Javalite is in
\figref{fig:surface-syntax} with the machine syntax (state) in
\figref{fig:machine-syntax}. Terminals are in bold face while
non-terminals are italicized. Ellipses indicate zero or more
repetitions. Tuples omit the commas for compactness. The language
itself uses s-expressions for convenience.

@@

A Javalite program, $\cfgnt{P}$, is a registry of classes, $\mu$, with
a tuple indicating a class, $\cfgnt{C}$, and a method, $\cfgnt{m}$,
where execution starts. The only primitive type in Javalite is
Boolean. Classes have fields, $([\cfgnt{T}\ \cfgnt{f}]\ ...)$, and
methods, $(\cfgnt{M}\ ...)$. Methods only take a single
parameter. Expressions, $\cfgnt{e}$, are somewhat typical with
$\cfgt{:=}$ indicating assignment, $\cfgt{=}$ indicating comparison,
$\cfgt{\$}$ as the dot-operator for field access, and $\cfgt{@}$ as
the dot-operator for method invocation. There is no explicit return
statement in Javalite; rather, the value of the last expression is
used as a return value. A variable is always indicated by \cfgnt{x}
and a value by \cfgnt{v}. A value can be a reference in the heap,
$\cfgnt{r}$, or any of the special values. It is assumed that only
type correct programs are given as input to the machine.

The state of the Javalite machine (\figref{fig:machine-syntax}),
$\cfgnt{s}$, includes the program registry\footnote{The registry $\mu$
  is implied in the rewrite rules rather that states for
  compactness.}, a pair of functions defining the heap
$\lp\cfgnt{L}\ \cfgnt{R}\rp$, which is the store, a constraint,
$\phi$, defined over references in the heap, the environment, $\eta$,
for local variables, and the continuation $\cfgnt{k}$. The more
complex structures such as the environment are defined as lists which
start with empty, \cfgnt{mt}. The rewrite rules that define the
semantics treat these lists as partial functions. As such,
$\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference mapped to the variable
$\cfgnt{x}$. The notation $\eta^\prime = \eta[\cfgnt{x} \mapsto
  \cfgnt{v}]$ defines a new partial function $\eta^\prime$ that is
just like $\eta$ only the variable $\cfgnt{x}$ now maps to
$\cfgnt{v}$.

>>>>

\section{Background}
\subsection{Javalite}
We present our summary heap algorithm using Javalite, an
executable formalization of a Java-like language~\cite{saints-MS}. Javalite retains 
the essence of Java and other object-oriented languages with formalizations 
in both PLT Redex and Coq so that the outcome of any program has a precise
and deterministic meaning.

Javalite is a syntactic machine defined as rewrites on a string.  The
semantics are small-step using the CEKS model with a (C)ontrol string
representing the expression being evaluated, an (E)nvironment for
local variables, a (S)tore for the heap, and a (K)ontinuation for what
is to be executed next.  In this work we change the semantics of the original
 Javalite machine and its machine syntax to represent (i) generalized
symbolic execution~\cite{GSE03}, and (ii) the summary heap algorithm
presented in this work.

The surface syntax (input) for Javalite is shown 
in~\figref{fig:surface-syntax}, and the machine syntax (state)
in~\figref{fig:machine-syntax}. Terminals are in bold face while
non-terminals are italicized. Ellipses indicate zero or more
repetitions. Tuples omit the commas for compactness. The language
itself uses s-expressions for convenience.

@@

A Javalite program, $\cfgnt{P}$, is a registry of classes, $\mu$, with
a tuple indicating a class, $\cfgnt{C}$, and a method, $\cfgnt{m}$,
where execution starts. The only primitive type in Javalite is
Boolean. Classes have fields, $([\cfgnt{T}\ \cfgnt{f}]\ ...)$, and
methods, $(\cfgnt{M}\ ...)$. Methods are limited to a single
parameter in our Javalite machine. Expressions, $\cfgnt{e}$, are 
equivalent to a CEKS machine's control string, 
%somewhat typical
where $\cfgt{:=}$ indicates assignment, $\cfgt{=}$ indicates comparison,
and $\cfgt{\$}$ represents the dot-operator for field access. The dot-operator
for method invocation is represented by $\cfgt{@}$. There is no explicit return
statement in Javalite; rather, the value of the last expression is
used as the return value. A variable is always indicated by \cfgnt{x}
and a value by \cfgnt{v}. A value can be a reference in the heap,
$\cfgnt{r}$, or any of the special values shown in~\figref{fig:surface-syntax}. 
We assume that only
type correct programs are given as input to the machine.

The state of the Javalite machine (\figref{fig:machine-syntax}),
$\cfgnt{s}$, includes the program registry, $\mu$\footnote{The registry $\mu$
  is implied in the rewrite rules and not included in the state tuples.},
  and a pair of functions defining the heap
$\lp\cfgnt{L}\ \cfgnt{R}\rp$, which is the store. The state also
includes a constraint,
$\phi$, defined over references in the heap, the environment, $\eta$,
for local variables, and the continuation $\cfgnt{k}$. The more
complex structures, such as the environment, are defined as lists which
start with empty, \cfgnt{mt}. The rewrite rules that define the
semantics treat these lists as partial functions. As such,
$\eta(\cfgnt{x}) = \cfgnt{r}$ is the reference $\cfgnt{r}$ mapped to the variable
$\cfgnt{x}$. The notation $\eta^\prime = \eta[\cfgnt{x} \mapsto
  \cfgnt{v}]$ defines a new partial function $\eta^\prime$ that is
the same as $\eta$ except that the variable $\cfgnt{x}$ now maps to
$\cfgnt{v}$.
